Forecasting the 2024 U.S. Presidential Election through Poll Aggregation and Adjustments for Poll Quality

### 2024-11-04 paper/paper.qmd
fixed figure formatting
Update paper.qmd

---
title: "Forecasting the 2024 U.S. Presidential Election through Poll Aggregation and Adjustments for Poll Quality"
subtitle: "A Hybrid Model Predicts a Narrow Lead for Kamala Harris in Swing States as Election Day Approaches"
author: 
  - Colin Sihan Yang
  - Lexun Yu
  - Siddharth Gowda
thanks: "Code and data are available at: [https://github.com/yulexun/uselection](https://github.com/yulexun/uselection)."
date: today
date-format: long
abstract: "This paper develops a hybrid model to forecast the 2024 U.S. presidential election by combining poll aggregation techniques with additional variables, including pollster reliability, sample size, timing relative to the election, geographic region, and polling methodology. By integrating these factors, our model accounts for variations in poll quality and regional differences in voter sentiment, providing a more stable and accurate prediction compared to traditional poll aggregation alone. Our results show that Kamala Harris holds a slight lead over Donald Trump in most swing states, with support levels stabilizing closer to election day. This approach reveals how poll quality and timing can significantly influence support predictions. This model offers a comprehensive tool for understanding the dynamics of voter sentiment and improving the accuracy of election predictions. "
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election through Poll Aggregation and Adjustments for Poll Quality"
subtitle: "A Hybrid Model Predicts a Lead for Kamala Harris in Swing States as Election Day Approaches"
author: 
  - Colin Sihan Yang
  - Lexun Yu
  - Siddharth Gowda
thanks: "Code and data are available at: [https://github.com/yulexun/uselection](https://github.com/yulexun/uselection)."
date: today
date-format: long
abstract: "This paper develops a hybrid model to forecast the 2024 U.S. presidential election by combining poll aggregation techniques with additional variables, including pollster reliability, sample size, timing relative to the election, geographic region, and polling methodology. By integrating these factors, our model accounts for variations in poll quality and regional differences in voter sentiment, providing a more stable and accurate prediction compared to traditional poll aggregation alone. Our results show that Kamala Harris holds a slight lead over Donald Trump in most swing states, with support levels stabilizing closer to election day. This approach reveals how poll quality and timing can significantly influence support predictions. This model offers a comprehensive tool for understanding the dynamics of voter sentiment and improving the accuracy of election predictions. "
format: pdf
number-sections: true
bibliography: references.bib
---
